---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 
Import the libraries
```{r}
library(lubridate)
library(tidyverse)
library(RVerbalExpressions)
library(stringr)
```
# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
first_day <- ymd("2019-01-01")+months(0:11)
first_day
```

Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
get_age <- function(birthdate){
  year(today())-year(birthdate)
}
```

```{r}
birth = '1995-10-31'
get_age(birth)
```

Write a function that given your birthday, returns the day of the week you were born on. 
```{r}
get_weekday <- function(birthday){
 wday(birthday, label = TRUE, abbr = TRUE)
}
get_weekday('1995-10-31')
```

## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r}
# Regex Version
str_view(stringr::words, "[a-zA-Z]{7,}")
```
```{r}
# RVerbalexpressions
morethan_seven <- rx() %>% 
  rx_start_of_line() %>% 
  rx_any_of("a-zA-Z") %>% 
  rx_multiple(min = 7) %>% 
  rx_end_of_line()

str_view(stringr::words, morethan_seven)
```

## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r}
# Regex
words[str_detect(stringr::words, "^[^aeiou]+$")]
```
```{r}
# RVerbalexpressions
only_consonants <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but('aeiou') %>% 
  rx_end_of_line()
words[str_detect(stringr::words, only_consonants)]
```

Empirically verify the rule “i before e except after c”.
```{r}
# Regex
words[str_detect(stringr::words, "[^c]ie|cei")]
# There are 14 words which don't follow the rule
words[str_detect(stringr::words, "[^c]ei|cie")]
# There are 3 words which follow the rule
```
```{r}
# RVerbalexpressions
ie_rule <- rx() %>% 
  rx_either_of("cei", 
               rx() %>% 
                 rx_something_but("c") %>% 
                 rx_find("ie")
               )
words[str_detect(stringr::words, ie_rule)]
# There are 14 words which don't follow the rule
ie_rule <- rx() %>% 
  rx_either_of("cie", 
               rx() %>% 
                 rx_something_but("c") %>% 
                 rx_find("ei")
               )
words[str_detect(stringr::words, ie_rule)]
# There are 3 words which follow the rule
```

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}
# Regex Version
grepl("^\\d{3}[-\\.]\\d{3}[-\\.]\\d{4}$", c("201-713-7914", "201.713.7914"))
```
```{r}
# RVerbalexpressions
telrx <- rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>%
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  grepl(c("201-713-7914", "201.713-7914")) %>% 
  print()
```

# Part 2
Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

