---
title: "Data Cleaning"
output:
  html_document:
    df_print: paged
---
# About the servo dataset

This data set is from a simulation of a servo system involving a servo amplifier, a motor, a lead screw/nut, and a sliding carriage of some sort. It may have been on of the translational axes of a robot on the 9th floor of the AI lab. In any case, the output value is almost certainly a rise time, or the time required for the system to respond to a step change in a position set point. The variables that describe the data set and their values are the following:

Motor:	A,B,C,D,E
Screw:	A,B,C,D,E
Pgain:	3,4,5,6
Vgain:	1,2,3,4,5
Class:	0.13 to 7.10
# The predictive modeling problem

I would like to investigate if we can use the variables Motor, Screw, Pgain and Vgain to predict the Class of servo by using regression.

# Import the dataset servo

```{r library_import}
library(readr)
library(tidyverse)
library(assertr)
Servo <- read_csv("Servo.csv")
```
# Test each variable

```{r str_check}
Servo %>% 
  str()
```
```{r summary_check}
Servo %>% 
  summary()
```
```{r Motor_test}
Servo %>% 
  assert(in_set("A","B","C","D","E"), Motor)
```
Looks great!

```{r Screw_test}
Servo %>% 
  assert(in_set("A","B","C","D","E"), Screw)
```
Looks great!

```{r Pgain_test}
Servo %>% 
  assert(in_set(3,4,5,6), Pgain)
```
Looks great!

```{r Vgain_test}
Servo %>% 
  assert(in_set(1,2,3,4,5), Vgain)
```
Looks great!

```{r Class_test, error=TRUE}
Servo %>% 
  assert(within_bounds(0.13, 7.10), Class)
```
Whoops!  It seems like most of the observations have the Class value in the invalid range!  

# Data Cleaning

We assume that this column has been timed 10, so we just divide the values by 10 and we'll select the records with valid Class value.
```{r data_clean}
Servo <- Servo %>% 
  mutate(Class = Class/10) %>% 
  filter(Class > 0.13, Class < 7.1)
```

Then we group the dataset and make it odered
```{r data_order}
Servo %>% 
  arrange(Motor, Screw, Pgain, Vgain)
```
# Feature engineering
```{r functions_define}
scales2 <- function(x){
  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
}
class_mean <- function(df, vars){
  df %>% 
    group_by(Motor, Screw) %>% 
    mutate(mean_class = mean({{vars}}, na.rm = TRUE)) %>% 
    ungroup() 
}
class_max <- function(df, vars){
  df %>% 
    group_by(Motor, Screw) %>% 
    mutate(max_class = max({{vars}})) %>% 
    ungroup() 
}
class_min<- function(df, vars){
  df %>% 
    group_by(Motor, Screw) %>% 
    mutate(min_class = min({{vars}})) %>% 
    ungroup() 
}
class_std <- function(df, vars){
  df %>% 
    group_by(Motor, Screw) %>% 
    mutate_at(vars, list(std_class = scales2)) %>% 
    ungroup() 
}
```

```{r features_create}
featured_Servo <- Servo %>% 
  class_mean(Class) %>% 
  class_max(Class) %>% 
  class_min(Class) %>% 
  class_std(c('Class'))
```

```{r features_test}
# Test the features
featured_Servo %>% 
  assert(within_bounds(0.13, 7.10), max_class)

featured_Servo %>% 
  assert(within_bounds(0.13, 7.10), min_class)

featured_Servo %>% 
  assert(within_bounds(0.13, 7.10), mean_class)
```

# Prepare the data for modeling
```{r data_prepare}
# The dataset has been cleaned and it's ready for applying the model.
modeling_data <- Servo
```

