---
title: "Data Preprocess"
output:
  html_document:
    df_print: paged
---
# About the breast cancer dataset

This breast cancer databases was obtained from the University of Wisconsin Hospitals, it contains 10 attributes include 9 cell indication attributes and 1 label attributes which shows if the cancer cell is benign or not.

1. Sample code number: id number
2. Clump Thickness: 1 - 10
3. Uniformity of Cell Size: 1 - 10
4. Uniformity of Cell Shape: 1 - 10
5. Marginal Adhesion: 1 - 10
6. Single Epithelial Cell Size: 1 - 10
7. Bare Nuclei: 1 - 10
8. Bland Chromatin: 1 - 10
9. Normal Nucleoli: 1 - 10
10. Mitoses: 1 - 10
11. Class: (2 for benign, 4 for malignant)
# The predictive modeling problem

I would like to investigate if we can use those 9 indication attrbutes to predict if the patient have cancer.

# Import the dataset servo

```{r library_import}
library(readr)
library(tidyverse)
library(assertr)
bc_data <- read_csv("BreastCancer.csv")
```
# Preview the structure of the dataset

```{r str_check}
bc_data %>% 
  str()
```
```{r summary_check}
bc_data %>% 
  summary()
```

# Data cleaning and testing
```{r drop_Id}
bc_data <- bc_data %>% 
  select(-Id)
```

```{r drop_na}
bc_data <- bc_data %>% 
  drop_na()
```

# Test each feature
```{r test_feature}
bc_data %>% 
  assert(within_bounds(1,10), Cl.thickness) %>% 
  assert(within_bounds(1,10), Cell.size) %>% 
  assert(within_bounds(1,10),Cell.shape) %>% 
  assert(within_bounds(1,10), Marg.adhesion) %>% 
  assert(within_bounds(1,10), Epith.c.size) %>% 
  assert(within_bounds(1,10), Bare.nuclei) %>% 
  assert(within_bounds(1,10), Bl.cromatin) %>% 
  assert(within_bounds(1,10), Normal.nucleoli) %>% 
  assert(within_bounds(1,10), Mitoses) %>% 
  assert(in_set("benign", "malignant"), Class)
  
```

# Data cleaning
## For here, I would like to change the variable "Class" to "0" or "1"
```{r define_label}
bc_data <- bc_data %>% 
  mutate(Cancer = ifelse(Class == "malignant", 1, 0)) %>% 
  select(everything(), -Class)
```
The dataset is much cleaner.

# Feature engineering

I would like to see the difference of each patient's numeric indication from the normal value, it will help us figure out the abnormal parts, however, we do not have the normal value so we use the mean value. 
```{r diff_function_define}
cellsize_diff<- function(df){
  if (!"Cell.size" %in% names(df)) {
    stop("data must contain 'Cell.size'")
  }
  df<- df %>% 
    mutate(cellsize_diff = Cell.size-mean(Cell.size))
}

cellthick_diff<- function(df){
  if (!"Cl.thickness" %in% names(df)) {
    stop("data must contain 'Cl.thickness'")
  }
  df<- df %>% 
    mutate(cellthick_diff = Cl.thickness-mean(Cl.thickness))
}

epithcellsize_diff<- function(df){
  if (!"Epith.c.size" %in% names(df)) {
    stop("data must contain 'Epith.c.size'")
  }
  df<- df %>% 
    mutate(epithcellsize_diff = Epith.c.size-mean(Epith.c.size))
}

```
 
## Test those functions
```{r test_diff_funciton}
data <- cellsize_diff(bc_data) %>% 
  cellthick_diff() %>% 
  epithcellsize_diff() %>% 
  select(contains("_diff"), everything())
data
```
As we can see, those features are working.

## Standardize function

I would like to standarlize all the numeric attributes to erase the affect of the outlier values.
```{r define_std_function}
scales_form <- function(x){
  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
}

std_var <- function(df, vars){
  df %>% 
    mutate_at(vars, list(std_cell = scales_form)) %>% 
    select(contains("_cell"), everything())
}
```

## Test the standardize function
```{r test_std_function}
data <- data %>% 
std_var(c("cellsize_diff", "cellthick_diff", "epithcellsize_diff", "Cl.thickness", "Cell.size", "Epith.c.size"))

data
```
Looks great!

# Prepare the data for modeling

```{r}
model_data <- data %>% 
  select(everything(),-Cell.size,-Cl.thickness, -Epith.c.size, -cellsize_diff, -cellthick_diff, -epithcellsize_diff)

model_data
```
## Split the data into train data and test data
```{r split_data}
set.seed(1031)
train_sub <- sample(nrow(model_data),0.7*nrow(model_data))
train_set <- model_data[train_sub,]
val_test_set <- model_data[-train_sub,]
val_sub <- sample(nrow(val_test_set), 0.5*nrow(val_test_set))
val_set <- val_test_set[val_sub,]
test_set <- val_test_set[-val_sub,]
```

